### 2021-12-02 input/experiments.tex
adapting to two columns, stilltodo. simpler problem display
reorder again, mb better, todiscuss
include figure of what it could look like to have xascast experiment

\newcommand{\FIGSCALE}{0.59}

@@

This section aims to answer the following questions about \NAME: What
is the overhead of reaching consistent partitioning using \NAME in
large scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\url{https://anonymous.4open.science/r/peersim-partition-5592}.

@@

>>>>

\newcommand{\FIGSCALE}{0.99}

@@

This section aims to answer the following questions about \NAME: What
is the overhead of reaching consistent partitioning using \NAME in
large scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.

@@

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe. The generated trace marked with red dots starts from
    Lisboa to reach Copenhagen 10 seconds later.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:xascast}\TODO{PLACEHOLDER}
    \TODO{Experiment with ascast against xascast?}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.}}
\end{figure*}

### 2021-12-02 input/proposal.tex
include figure of what it could look like to have xascast experiment

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest broadcast of a \node matters.  A message $m$ conveys
  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
  \process only sends messages that it assumes up-to-date:
  $s_x(\alpha_s) \implies \delta_s \not\in R_x$.
\end{definition}

@@

\begin{proof}
  \TODO{Meow.}
\end{proof}

>>>>

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest broadcast of a \node matters.  A message $m$ conveys
  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
  \process only sends messages that it assumes up-to-date:
  $s_x(\alpha_s) \implies \delta_s \not\in R_x$. \TODO{Only keep last?
    Tothink what happens if we keep all as in def now.}
\end{definition}

@@

\begin{proof}
  Detection triggers forwarding of staleness downstream which
  completes the case study of Lemma~\ref{lem:detector} by ensuring
  that, when a source broadcasts its staleness notification, all
  \processes that belong to its partition eventually deliver such a
  staleness notification. All downstream bordering \processes also
  eventually receive such a staleness notification and echo back their
  best delivered message. This triggers another competition as in
  Theorem~\ref{theo:fb} for the \processes that delivered the
  staleness notification.
\end{proof}
